Results

### 2018-07-13 4-results-simus.Rmd
save

```{r}
myggplot <- function(..., coeff = 1) {
  bigstatsr:::MY_THEME(ggplot(...), coeff = coeff) +
  theme(strip.text.x = element_text(size = rel(2)),
        strip.text.y = element_text(size = rel(2)))
} 
```

>>>>

```{r}
myggplot <- function(..., coeff = 1) {
  ggplot(...) + 
    bigstatsr::theme_bigstatsr(size.rel = coeff) +
    theme(strip.text.x = element_text(size = rel(2)),
          strip.text.y = element_text(size = rel(2)))
} 
```
